A fault tolerant multi-server system for MMOGs

### 2010-11-08 trunk/textos/phd-prospectus/prospectus.tex

As proposed in [cite related work], it is used here the idea of \textbf{contact servers} and \textbf{target servers}. In our architecture, the players whose avatars are in a certain region are distributed among the server nodes responsible for that region. The distribution is decided based on the network latency for each pair client-server. Each client is assigned to a server to which it has the lowest network latency among all servers in its region. This server, to which the client communicates directly, is its contact server. The target server is always the region manager, which can also be the contact server for certain players. When one of the servers gets overloaded because of the broadcasting of messages to players, these messages are then sent via other routes, even if the network latency of that new route is higher.

When a player issues a command, it is sent to its contact server, which forwards the command to the region manager. The region manager then processes the command sent by the player and calculates its resulting state, also considering commands sent by other players. Any prior event that the contact server should be aware of and that has not been received by the contact server of that player yet is then sent by the region manager.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proposed synchronization algorithm} \label{sec:algorithm}

y

>>>>

As proposed in [cite related work], it is used here the idea of \textbf{contact servers} and \textbf{target servers}. In our architecture, the players whose avatars are in a certain region are distributed among the server nodes responsible for that region. The distribution is decided based on the network latency for each pair client-server. Each client is assigned to a server to which it has the lowest network latency among all servers in its region. This server, to which the client communicates directly, is its contact server. The target server is always the region manager, which can also be the contact server for certain players. When one of the servers gets overloaded because of the broadcasting of messages to players, these messages are then sent via other routes, even if the network latency of that new route is higher. Figure \ref{fig:arch} illustrates this architecture.

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.45\linewidth]{images/arch}
	\caption{Basic architecture with Region Managers and Region Replicas}
	\label{fig:arch}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proposed causality definition and synchronization algorithm} \label{sec:algorithm}

When a player issues a command $c_{i}$, it is sent to its contact server, which forwards the command to the region manager. The region manager then processes the command sent by the player and calculates its resulting state, also considering every command -- or any kind of event -- $c_{j}$ sent by other players, such that $c_{j}$ was issued prior to $c_{i}$. Any prior event $c_{j}$ that the contact server should be aware of and that has not been received by the contact server of that player yet is then sent by the region manager. By having these prior events, the contact server is able to calculate the new game state that should be sent to the player who issued the command $c_{i}$.

The \textbf{causality} is defined here based on which objects are affected by an event. If commands $e_{i}$ and $e_{j}$ affect the same object, then they must be ordered. The order is defined by the time when they are delivered at the region manager responsible for that object.

@@
